### 2023-07-19 python_excel_ite.tex
updated readme

\begin{figure*}[!htbp]
	\centering
	\caption{Notebook cells in edit model}
	\includegraphics[scale=1.0]{images/cells_edit_mode.png}
	\label{fig:cells_edit_mode}
\end{figure*}

\begin{figure*}[!htbp]
	\centering
	\caption{Notebook cells after execution}
	\includegraphics[scale=1.0]{images/cells_after_running.png}
	\label{fig:cells_after_running}
\end{figure*}

@@

There is also a [whatif Github repository](https://github.com/misken/whatif) for the \code{whatif} package. It also contains the original notebooks used in the blog posts that motivated this project.

>>>>

\begin{figure*}[!htbp]
	\centering
	\caption{Notebook cells in edit model}
	\includegraphics[scale=0.5]{images/cells_edit_mode.png}
	\label{fig:cells_edit_mode}
\end{figure*}

\begin{figure*}[!htbp]
	\centering
	\caption{Notebook cells after execution}
	\includegraphics[scale=0.5]{images/cells_after_running.png}
	\label{fig:cells_after_running}
\end{figure*}

@@

There is also a \href{https://github.com/misken/whatif}{whatif Github repository} for the \code{whatif} package. It also contains the original notebooks used in the blog posts that motivated this project.
